---
title: "MLB PLAYOFFS 2018 KBS 1.1"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

```


```{r include=FALSE}
```


```{r echo = FALSE}
MLB2018r <- subset(mlb_elo, season == "2018")

MLB2018 <- MLB2018r %>% clean_names() %>% mutate( team1 = as.factor(team1), team2 = as.factor(team2))
```


```{r echo = FALSE}
YANKS18H <- subset(MLB2018, team1 == "NYY", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

YANKS18A <- subset(MLB2018, team2 == "NYY", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

OAK18H <- subset(MLB2018, team1 == "OAK", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

OAK18A <- subset(MLB2018, team2 == "OAK", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))
```


#***Wild Card Games***


##***Yankees vs. A's***
###*$161,305,917 vs. $62,652,500*
```{r echo = FALSE}
YANKSHRs   <- MLB2018[MLB2018$team1=="NYY", "score1"]
YANKSHRa   <- MLB2018[MLB2018$team1=="NYY", "score2"]
YANKSARs   <- MLB2018[MLB2018$team2=="NYY", "score2"]
YANKSARa   <- MLB2018[MLB2018$team2=="NYY", "score1"]
NYYRsMELT  <- melt(c(YANKSHRs, YANKSARs), na.rm = TRUE)
NYYRaMELT  <- melt(c(YANKSHRa, YANKSARa), na.rm = TRUE)
NYYRs      <- data.frame(NYYRsMELT$value)
NYYRa      <- data.frame(NYYRaMELT$value)

LSnyyHRs   <- MLB2018[MLB2018$pitcher1=="Luis Severino", "score1"]
LSnyyHRa   <- MLB2018[MLB2018$pitcher1=="Luis Severino", "score2"]
LSnyyARs   <- MLB2018[MLB2018$pitcher2=="Luis Severino", "score2"]
LSnyyARa   <- MLB2018[MLB2018$pitcher2=="Luis Severino", "score1"]
LSnyyRMELT <- melt(c(LSnyyHRs, LSnyyARs), na.rm = TRUE)
LSnyyAMELT <- melt(c(LSnyyHRa, LSnyyARa), na.rm = TRUE)
LSnyyRs    <- data.frame(LSnyyRMELT$value)
LSnyyRa    <- data.frame(LSnyyAMELT$value)

OAKHRs     <- MLB2018[MLB2018$team1=="OAK", "score1"]
OAKHRa     <- MLB2018[MLB2018$team1=="OAK", "score2"]
OAKARs     <- MLB2018[MLB2018$team2=="OAK", "score2"]
OAKARa     <- MLB2018[MLB2018$team2=="OAK", "score1"]
OAKRsMELT  <- melt(c(OAKHRs, OAKARs), na.rm = TRUE)
OAKaMELT   <- melt(c(OAKHRa, OAKARa), na.rm = TRUE)
OAKRs      <- data.frame(OAKRsMELT$value)
OAKRa      <- data.frame(OAKaMELT$value)

LHoakHRs   <- MLB2018[MLB2018$pitcher1=="Liam Hendriks", "score1"]
LHoakHRa   <- MLB2018[MLB2018$pitcher1=="Liam Hendriks", "score2"]
LHoakARs   <- MLB2018[MLB2018$pitcher2=="Liam Hendriks", "score2"]
LHoakARa   <- MLB2018[MLB2018$pitcher2=="Liam Hendriks", "score1"]
LHoakRMELT <- melt(c(LHoakHRs, LHoakARs), na.rm = TRUE)
LHoakAMELT <- melt(c(LHoakHRa, LHoakARa), na.rm = TRUE)
LHoakRs    <- data.frame(LHoakRMELT$value)
LHoakRa    <- data.frame(LHoakAMELT$value)
```

```{r echo = FALSE}
print.noquote("New York SaberWin%")
sabermtrkk.WP(NYYRs, NYYRa)
print.noquote("Oakland As Saberwin%")
sabermtrkk.WP(OAKRs, OAKRa)
print.noquote("Luis Severino SaberWin%")
sabermtrkk.WP(LSnyyRs, LSnyyRa)
print.noquote("Liam Hendricks SaberWin%")
sabermtrkk.WP(LHoakRs, LHoakRa)
```




```{r echo = FALSE}
boxplot(c(NYYRa, OAKRa, NYYRs, OAKRs), horizontal = TRUE, names = c("NYY.RA", "OAK.RA", "NYY.Rs", "OAK.Rs"), main = "Yankees/A's", sub = "Runs Scored vs. Runs Allowed", col = c( "#0C2340", "#003831", "#0C2340", "#003831"), notch = TRUE, outline = FALSE, border = "goldenrod")
```




```{r echo = FALSE}
NYY18OAK     <- subset(YANKS18H, team2=="OAK", select = c(date, team1, team2, pitcher1, pitcher2, score1, score2), na.rm = TRUE)

OAK18NYY     <- subset(YANKS18A, team1=="OAK", select = c(date, team1, team2, pitcher1, pitcher2, score1, score2))

OAKvYANKS    <- melt(c(NYY18OAK$score1, OAK18NYY$score2))

YANKSvOAK    <- melt(c(NYY18OAK$score2, OAK18NYY$score1))
```

```{r echo = FALSE}
boxplot(c(OAKvYANKS, YANKSvOAK), horizontal = TRUE, names = c("OAK", "NYY"), main = "OAK vs NYY '18", sub = "Runs Scored against eachother", col = c("#003831", "#0C2340"), border = "goldenrod")
```



Average Runs Scored by the Yankees and Oakland against each other

```{r echo = FALSE}
print.noquote("OAK")
mean(OAKvYANKS$value, na.rm = TRUE)
print.noquote("NYY")
mean(YANKSvOAK$value, na.rm = TRUE)
```

###Result

####NYY 7 OAK 6


```{r}
CHCvCOLnlwc <- PSViewrrQF.KBS("CHC", "COL", "2018", "1")
CHCvCOLnlwc
```

```{r}
CHCHRs   <- MLB2018[MLB2018$team1=="CHC", "score1"]
CHCHRa   <- MLB2018[MLB2018$team1=="CHC", "score2"]
CHCARs   <- MLB2018[MLB2018$team2=="CHC", "score2"]
CHCARa   <- MLB2018[MLB2018$team2=="CHC", "score1"]
CHCRsMELT  <- melt(c(CHCHRs, CHCARs), na.rm = TRUE)
CHCRaMELT  <- melt(c(CHCHRa, CHCARa), na.rm = TRUE)
CHCRs      <- data.frame(CHCRsMELT$value)
CHCRa      <- data.frame(CHCRaMELT$value)

LSchcHRs   <- MLB2018[MLB2018$pitcher1=="Jon Lester", "score1"]
LSchcHRa   <- MLB2018[MLB2018$pitcher1=="Jon Lester", "score2"]
LSchcARs   <- MLB2018[MLB2018$pitcher2=="Jon Lester", "score2"]
LSchcARa   <- MLB2018[MLB2018$pitcher2=="Jon Lester", "score1"]
LSchcRMELT <- melt(c(LSchcHRs, LSchcARs), na.rm = TRUE)
LSchcAMELT <- melt(c(LSchcHRa, LSchcARa), na.rm = TRUE)
LSchcRs    <- data.frame(LSchcRMELT$value)
LSchcRa    <- data.frame(LSchcAMELT$value)
```


```{r}
CHC18H <- subset(MLB2018, team1 == "CHC", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

CHC18A <- subset(MLB2018, team2 == "CHC", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))


CHC18COL     <- subset(CHC18H, team2=="COL", select = c(date, team1, team2, pitcher1, pitcher2, score1, score2), na.rm = TRUE)

COL18CHC     <- subset(CHC18A, team1=="COL", select = c(date, team1, team2, pitcher1, pitcher2, score1, score2))

COLvCHC      <- melt(c(CHC18COL$score1, COL18CHC$score2))

CHCvCOL      <- melt(c(CHC18COL$score2, COL18CHC$score1))
```

```{r}
boxplot(c(COLRa, CHCRa, COLRs, CHCRs), horizontal = TRUE, names = c("COL.RA", "CHC.RA", "COL.Rs", "CHC.Rs"), main = "Rockies and Cubs 2018 Season", sub = "Runs Scored vs. Runs Allowed", col = c( "#33006F", "#0E3386", "#33006F", "#0E3386"), notch = TRUE, outline = FALSE, border = "black")
```

```{r}
boxplot(c(COLvCHC, CHCvCOL), horizontal = TRUE, names = c("COL","CHC"), main = "Rockies vs Cubs '18", sub = "Runs Scored against eachother", col = c("#33006F", "#0E3386"), border = "black", outline = F)
```

```{r}
print.noquote("Cubs, Jon Lester")
sabermtrkk.WP(CHCRs, CHCRa)
PitcherSBWsea.KBS("Jon Lester", "2018")
print.noquote("Rockies, Kyle Freeland")
sabermtrkk.WP(COLRs, COLRa)
PitcherSBWsea.KBS("Kyle Freeland", "2018")
```



#&nbsp;

#&nbsp;

#&nbsp;


#***American League Division Series***

##*Yankees @ Red Sox*

```{r echo = FALSE}
#Red Sox 

REDSOX18H <- subset(MLB2018, team1 == "BOS", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

REDSOX18A <- subset(MLB2018, team2 == "BOS", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

BosRHRs    <- MLB2018[MLB2018$team1=="BOS", "score1"]
BosRHRa    <- MLB2018[MLB2018$team1=="BOS", "score2"]
BosRARs    <- MLB2018[MLB2018$team2=="BOS", "score2"]
BosRARa    <- MLB2018[MLB2018$team2=="BOS", "score1"]
BOSRsMELT  <- melt(c(BosRHRs, BosRARs), na.rm = TRUE)
BOSRaMELT  <- melt(c(BosRHRa, BosRARa), na.rm = TRUE)
BOSRs      <- data.frame(BOSRsMELT$value)
BOSRa      <- data.frame(BOSRaMELT$value)

#RED SOX PITCHERS
#Chris Sale
CSbosHRs   <- MLB2018[MLB2018$pitcher1=="Chris Sale", "score1"]
CSbosHRa   <- MLB2018[MLB2018$pitcher1=="Chris Sale", "score2"]
CSbosARs   <- MLB2018[MLB2018$pitcher2=="Chris Sale", "score2"]
CSbosARa   <- MLB2018[MLB2018$pitcher2=="Chris Sale", "score1"]
CSbosRMELT <- melt(c(CSbosHRs, CSbosARs), na.rm = TRUE)
CSbosAMELT <- melt(c(CSbosHRa, CSbosARa), na.rm = TRUE)
CSbosRs    <- data.frame(CSbosRMELT$value)
CSbosRa    <- data.frame(CSbosAMELT$value)

#David Price
DPbosHRs   <- MLB2018[MLB2018$pitcher1=="David Price", "score1"]
DPbosHRa   <- MLB2018[MLB2018$pitcher1=="David Price", "score2"]
DPbosARs   <- MLB2018[MLB2018$pitcher2=="David Price", "score2"]
DPbosARa   <- MLB2018[MLB2018$pitcher2=="David Price", "score1"]
DPbosRMELT <- melt(c(DPbosHRs, DPbosARs), na.rm = TRUE)
DPbosAMELT <- melt(c(DPbosHRa, DPbosARa), na.rm = TRUE)
DPbosRs    <- data.frame(DPbosRMELT$value)
DPbosRa    <- data.frame(DPbosAMELT$value)

#Rick Porcello
RPbosHRs   <- MLB2018[MLB2018$pitcher1=="Rick Porcello", "score1"]
RPbosHRa   <- MLB2018[MLB2018$pitcher1=="Rick Porcello", "score2"]
RPbosARs   <- MLB2018[MLB2018$pitcher2=="Rick Porcello", "score2"]
RPbosARa   <- MLB2018[MLB2018$pitcher2=="Rick Porcello", "score1"]
RPbosRMELT <- melt(c(RPbosHRs, RPbosARs), na.rm = TRUE)
RPbosAMELT <- melt(c(RPbosHRa, RPbosARa), na.rm = TRUE)
RPbosRs    <- data.frame(RPbosRMELT$value)
RPbosRa    <- data.frame(RPbosAMELT$value)

#Yankees Pitchers
#J.A. Happ
JHnyyHRs   <- MLB2018[MLB2018$pitcher1=="J.A. Happ", "score1"]
JHnyyHRa   <- MLB2018[MLB2018$pitcher1=="J.A. Happ", "score2"]
JHnyyARs   <- MLB2018[MLB2018$pitcher2=="J.A. Happ", "score2"]
JHnyyARa   <- MLB2018[MLB2018$pitcher2=="J.A. Happ", "score1"]
JHnyyRMELT <- melt(c(JHnyyHRs, JHnyyARs), na.rm = TRUE)
JHnyyAMELT <- melt(c(JHnyyHRa, JHnyyARa), na.rm = TRUE)
JHnyyRs    <- data.frame(JHnyyRMELT$value)
JHnyyRa    <- data.frame(JHnyyAMELT$value)

#Masahiro Tanaka
MTnyyHRs   <- MLB2018[MLB2018$pitcher1=="Masahiro Tanakap", "score1"]
MTnyyHRa   <- MLB2018[MLB2018$pitcher1=="Masahiro Tanaka", "score2"]
MTnyyARs   <- MLB2018[MLB2018$pitcher2=="Masahiro Tanaka", "score2"]
MTnyyARa   <- MLB2018[MLB2018$pitcher2=="Masahiro Tanaka", "score1"]
MTnyyRMELT <- melt(c(MTnyyHRs, MTnyyARs), na.rm = TRUE)
MTnyyAMELT <- melt(c(MTnyyHRa, MTnyyARa), na.rm = TRUE)
MTnyyRs    <- data.frame(MTnyyRMELT$value)
MTnyyRa    <- data.frame(MTnyyAMELT$value)


#Yankees vs. Red Sox 2018
NYY18BOS     <- subset(YANKS18H, team2=="BOS", select = c(date, team1, team2, pitcher1, pitcher2, score1, score2), na.rm = TRUE)

BOS18NYY     <- subset(YANKS18A, team1=="BOS", select = c(date, team1, team2, pitcher1, pitcher2, score1, score2), na.rm = TRUE)

BOSvNYY      <- melt(c(NYY18BOS$score1, BOS18NYY$score2))

NYYvBOS      <- melt(c(NYY18BOS$score2, BOS18NYY$score1))
```


```{r}
BOSvNYY18DS <- mlb_elo %>%
  select(date, season, playoff, team1, team2, pitcher1, pitcher2, score1, score2) %>%
  filter(playoff == "2") %>%
  filter(team1 == "BOS" | team1 == "NYY") %>%
  filter(season == "2018") %>%
  arrange(date) %>%
  select(date, team1, team2, pitcher1, pitcher2, score1, score2)

BOSvNYY18DS
```

#&nbsp;

####Sabermetric Win Percentage
```{r echo = FALSE}
print.noquote("Boston")
sabermtrkk.WP(BOSRs, BOSRa)
print.noquote("Yankees")
sabermtrkk.WP(NYYRs, NYYRa)
```
#&nbsp;


```{r echo = FALSE}
boxplot(c(NYYRa, BOSRa, NYYRs, BOSRs), horizontal = TRUE, names = c("NYY.RA", "BOS.RA", "NYY.Rs", "BOS.Rs"), main = "Red Sox '18 Season and Yankes '18 Season", sub = "Runs Scored vs. Runs Allowed", col = c( "#0C2340", "#BD3039", "#0C2340", "#BD3039"), notch = TRUE, outline = FALSE, border = "grey")

```
#&nbsp;

```{r echo = FALSE}
boxplot(c(BOSvNYY, NYYvBOS), horizontal = TRUE, names = c("BOS", "NYY"), main = "Red Sox vs. Yankees '18", sub = "Runs Scored against eachother", col = c("#BD3039", "#0C2340"), border = "grey")
```


#&nbsp;
####Friday @FENWAY
####*Chris Sale vs. J.A. Happ Sabermetric %*

```{r echo = FALSE}
print.noquote("Chris Sale")
sabermtrkk.WP(CSbosRs, CSbosRa)
print.noquote("J.A. Happ")
sabermtrkk.WP(JHnyyRs, JHnyyRa)
```
#####56% Red Sox Win / 44% Yankees Win
#&nbsp;
####Saturday @FENWAY
####*David Price vs. Masahiro Tanaka Sabermetric %*

```{r echo=FALSE}
print.noquote("David Price")
sabermtrkk.WP(DPbosRs, DPbosRa)
print.noquote("Masahiro Tanaka")
sabermtrkk.WP(MTnyyRs, MTnyyRa)
```
#####52% Red Sox Win / 48% Yankees Win
#&nbsp;
####Monday @ YANKEE STADIUM
####*Luis Severino vs. Rick Porcello*

```{r}
print.noquote("Luis Severino (NYY)")
sabermtrkk.WP(LSnyyRs, LSnyyRa)
print.noquote("Nathan Eovaldi (BOS)")
PitcherSBWsea.KBS("Nathan Eovaldi", "2018")
```
#####46% Red Sox Win / 54% Yankees Win
#&nbsp;
####Tuesday @ YANKEE STADIUM
####*CC Sabathia vs. Nathan Eovaldi*
```{r}
print.noquote("Rick Porcello")
PitcherSBWsea.KBS("Rick Porcello", "2018")
PitcherSBW.all.playoffs.KBS("Rick Porcello")
print.noquote("CC Sabathia")
PitcherSBWsea.KBS("CC Sabathia", "2018")
PitcherSBW.all.playoffs.KBS("CC Sabathia")
```
#####51% Red Sox Win / 49% Yankees Win
#&nbsp;
####Thursday @ FENWAY
####*TBD vs. TBD*
```{r}
print.noquote("TBD")
print.noquote("TBD")
#PitcherSBWsea.KBS("Nathan Eovaldi", "2018")
print.noquote("TBD")
print.noquote("TBD")
#PitcherSBWsea.KBS("CC Sabathia", "2018")
```


#&nbsp;


#&nbsp; 



##*Indians @ Astros*

```{r}
#Houston Home and Away
HOU18H <- subset(MLB2018, team1 == "HOU", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

HOU18A <- subset(MLB2018, team2 == "HOU", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

#Cleavland Home and Away
CLE18H <- subset(MLB2018, team1 == "CLE", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

CLE18A <- subset(MLB2018, team2 == "CLE", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))
```

#####Series Viewer
```{r}
CLEvHOU18DS <- mlb_elo %>%
  select(date, season, playoff, team1, team2, pitcher1, pitcher2, score1, score2) %>%
  filter(playoff == "2") %>%
  filter(team1 == "CLE" | team1 == "HOU") %>%
  filter(season == "2018") %>%
  arrange(date) %>%
  select(date, team1, team2, pitcher1, pitcher2, score1, score2)

CLEvHOU18DS
```

```{r}
#Teams Sabermetrics

#Astros Team
HOUHRs     <- MLB2018[MLB2018$team1=="HOU", "score1"]
HOUHRa     <- MLB2018[MLB2018$team1=="HOU", "score2"]
HOUARs     <- MLB2018[MLB2018$team2=="HOU", "score2"]
HOUARa     <- MLB2018[MLB2018$team2=="HOU", "score1"]
HOURsMELT  <- melt(c(HOUHRs, HOUARs), na.rm = TRUE)
HOURaMELT  <- melt(c(HOUHRa, HOUARa), na.rm = TRUE)
HOURs      <- data.frame(HOURsMELT$value)
HOURa      <- data.frame(HOURaMELT$value)

#Astros Starting Pitching Rotation
#Justin Verlander
JVhouHRs   <- MLB2018[MLB2018$pitcher1=="Justin Verlander", "score1"]
JVhouHRa   <- MLB2018[MLB2018$pitcher1=="Justin Verlander", "score2"]
JVhouARs   <- MLB2018[MLB2018$pitcher2=="Justin Verlander", "score2"]
JVhouARa   <- MLB2018[MLB2018$pitcher2=="Justin Verlander", "score1"]
JVhouRMELT <- melt(c(JVhouHRs, JVhouARs), na.rm = TRUE)
JVhouAMELT <- melt(c(JVhouHRa, JVhouARa), na.rm = TRUE)
JVhouRs    <- data.frame(JVhouRMELT$value)
JVhouRa    <- data.frame(JVhouAMELT$value)
#Gerrit Cole
GChouHRs   <- MLB2018[MLB2018$pitcher1=="Gerrit Cole", "score1"]
GChouHRa   <- MLB2018[MLB2018$pitcher1=="Gerrit Cole", "score2"]
GChouARs   <- MLB2018[MLB2018$pitcher2=="Gerrit Cole", "score2"]
GChouARa   <- MLB2018[MLB2018$pitcher2=="Gerrit Cole", "score1"]
GChouRMELT <- melt(c(GChouHRs, GChouARs), na.rm = TRUE)
GChouAMELT <- melt(c(GChouHRa, GChouARa), na.rm = TRUE)
GChouRs    <- data.frame(GChouRMELT$value)
GChouRa    <- data.frame(GChouAMELT$value)
#Dallas Keuchel
DKhouHRs   <- MLB2018[MLB2018$pitcher1=="Dallas Keuchel", "score1"]
DKhouHRa   <- MLB2018[MLB2018$pitcher1=="Dallas Keuchel", "score2"]
DKhouARs   <- MLB2018[MLB2018$pitcher2=="Dallas Keuchel", "score2"]
DKhouARa   <- MLB2018[MLB2018$pitcher2=="Dallas Keuchel", "score1"]
DKhouRMELT <- melt(c(DKhouHRs, DKhouARs), na.rm = TRUE)
DKhouAMELT <- melt(c(DKhouHRa, DKhouARa), na.rm = TRUE)
DKhouRs    <- data.frame(DKhouRMELT$value)
DKhouRa    <- data.frame(DKhouAMELT$value)

#Cleveland
CLEHRs     <- MLB2018[MLB2018$team1=="CLE", "score1"]
CLEHRa     <- MLB2018[MLB2018$team1=="CLE", "score2"]
CLEARs     <- MLB2018[MLB2018$team2=="CLE", "score2"]
CLEARa     <- MLB2018[MLB2018$team2=="CLE", "score1"]
CLERsMELT  <- melt(c(CLEHRs, CLEARs), na.rm = TRUE)
CLEaMELT   <- melt(c(CLEHRa, CLEARa), na.rm = TRUE)
CLERs      <- data.frame(CLERsMELT$value)
CLERa      <- data.frame(CLEaMELT$value)

#Cleveland Starting Pitching Rotation
#Corey Kluber
CKcleHRs   <- MLB2018[MLB2018$pitcher1=="Corey Kluber", "score1"]
CKcleHRa   <- MLB2018[MLB2018$pitcher1=="Corey Kluber", "score2"]
CKcleARs   <- MLB2018[MLB2018$pitcher2=="Corey Kluber", "score2"]
CKcleARa   <- MLB2018[MLB2018$pitcher2=="Corey Kluber", "score1"]
CKcleRMELT <- melt(c(CKcleHRs, CKcleARs), na.rm = TRUE)
CKcleAMELT <- melt(c(CKcleHRa, CKcleARa), na.rm = TRUE)
CKcleRs    <- data.frame(CKcleRMELT$value)
CKcleRa    <- data.frame(CKcleAMELT$value)
#Carlos Carrasco
CCcleHRs   <- MLB2018[MLB2018$pitcher1=="Carlos Carrasco", "score1"]
CCcleHRa   <- MLB2018[MLB2018$pitcher1=="Carlos Carrasco", "score2"]
CCcleARs   <- MLB2018[MLB2018$pitcher2=="Carlos Carrasco", "score2"]
CCcleARa   <- MLB2018[MLB2018$pitcher2=="Carlos Carrasco", "score1"]
CCcleRMELT <- melt(c(CCcleHRs, CCcleARs), na.rm = TRUE)
CCcleAMELT <- melt(c(CCcleHRa, CCcleARa), na.rm = TRUE)
CCcleRs    <- data.frame(CCcleRMELT$value)
CCcleRa    <- data.frame(CCcleAMELT$value)
#Mike Clevinger
MCcleHRs   <- MLB2018[MLB2018$pitcher1=="Mike Clevinger", "score1"]
MCcleHRa   <- MLB2018[MLB2018$pitcher1=="Mike Clevinger", "score2"]
MCcleARs   <- MLB2018[MLB2018$pitcher2=="Mike Clevinger", "score2"]
MCcleARa   <- MLB2018[MLB2018$pitcher2=="Mike Clevinger", "score1"]
MCcleRMELT <- melt(c(MCcleHRs, MCcleARs), na.rm = TRUE)
MCcleAMELT <- melt(c(MCcleHRa, MCcleARa), na.rm = TRUE)
MCcleRs    <- data.frame(MCcleRMELT$value)
MCcleRa    <- data.frame(MCcleAMELT$value)
```
#&nbsp;
####Sabermetric Win Percentage

```{r}
print.noquote("Astros")
sabermtrkk.WP(HOURs, HOURa)
print.noquote("Indians")
sabermtrkk.WP(CLERs, CLERa)
```

#&nbsp;

```{r}
boxplot(c(HOURa, CLERa, HOURs, CLERs), horizontal = TRUE, names = c("HOU.RA", "CLE.RA", "HOU.Rs", "CLE.Rs"), main = "Houston '18 Season and Cleavland '18 Season", sub = "Runs Scored vs. Runs Allowed", col = c( "#EB6E1F", "#E31937", "#EB6E1F", "#E31937"), notch = TRUE, outline = FALSE, border = "#0C2340")
```


```{r}
#Astros Vs. Indians 2018
HOU18CLE     <- subset(HOU18H, team2=="CLE", select = c(date, team1, team2, pitcher1, pitcher2, score1, score2), na.rm = TRUE)

CLE18HOU     <- subset(HOU18A, team1=="CLE", select = c(date, team1, team2, pitcher1, pitcher2, score1, score2))

HOUvCLE      <- melt(c(HOU18CLE$score1, CLE18HOU$score2))

CLEvHOU      <- melt(c(HOU18CLE$score2, CLE18HOU$score1))
```
#&nbsp;


```{r}
boxplot(c(HOUvCLE, CLEvHOU), horizontal = TRUE, names = c("HOU", "CLE"), main = "Houtson vs Cleavland '18", sub = "Runs Scored against eachother", col = c("#EB6E1F", "#E31937"), border = "#0C2340")
```
#&nbsp;

###Friday @Minute Maid Park

####*Corey Kluber vs. Justin Verlander %*

```{r}
print.noquote("Corey Kluber")
sabermtrkk.WP(CKcleRs, CKcleRa)
print.noquote("Justin Verlander")
sabermtrkk.WP(JVhouRs, JVhouRa)
```
#####64% Astro's Win / 36% Indians Win


#&nbsp;
###Saturday @Minute Maid Park

####*Carlos Carrasco vs. Gerrit Cole %*

```{r}
print.noquote("Carlos Carrasco")
sabermtrkk.WP(CCcleRs, CCcleRa)
print.noquote("Gerrit Cole")
sabermtrkk.WP(GChouRs, GChouRa)
```
#####70% Astro's Win / 30% Indians Win

#&nbsp;
###Monday at @Indians Field

####*Mike Clevinger vs. Dallas Keuchel %*

```{r}
print.noquote("Mike Clevinger (CLE)")
sabermtrkk.WP(MCcleRs, MCcleRa)
print.noquote("Dallas Keuchel (HOU)")
sabermtrkk.WP(DKhouRs, DKhouRa)
```
#####51% Astro's Win / 49% Indians Win

#&nbsp;

#&nbsp;


#***National League Division Series***

##*Rockies @ Brewers*


#####Series Viewer
```{r}
MILvCOL18DS <- mlb_elo %>%
  select(date, season, playoff, team1, team2, pitcher1, pitcher2, score1, score2) %>%
  filter(playoff == "2") %>%
  filter(team1 == "MIL" | team1 == "COL") %>%
  filter(season == "2018") %>%
  arrange(date) %>%
  select(date, team1, team2, pitcher1, pitcher2, score1, score2)

MILvCOL18DS

```


```{r}
#Teams home and away performance
MIL18H <- subset(MLB2018, team1 == "MIL", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

MIL18A <- subset(MLB2018, team2 == "MIL", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

COL18H <- subset(MLB2018, team1 == "COL", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

COL18A <- subset(MLB2018, team2 == "COL", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))
```


```{r}
#Brewers 

MIL18H <- subset(MLB2018, team1 == "MIL", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

MIL18A <- subset(MLB2018, team2 == "MIL", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

MILRHRs    <- MLB2018[MLB2018$team1=="MIL", "score1"]
MILRHRa    <- MLB2018[MLB2018$team1=="MIL", "score2"]
MILRARs    <- MLB2018[MLB2018$team2=="MIL", "score2"]
MILRARa    <- MLB2018[MLB2018$team2=="MIL", "score1"]
MILRsMELT  <- melt(c(MILRHRs, MILRARs), na.rm = TRUE)
MILRaMELT  <- melt(c(MILRHRa, MILRARa), na.rm = TRUE)
MILRs      <- data.frame(MILRsMELT$value)
MILRa      <- data.frame(MILRaMELT$value)

#Brewers PITCHERS
#Brandon Woodruff
BWmilHRs   <- MLB2018[MLB2018$pitcher1=="Brandon Woodruff", "score1"]
BWmilHRa   <- MLB2018[MLB2018$pitcher1=="Brandon Woodruff", "score2"]
BWmilARs   <- MLB2018[MLB2018$pitcher2=="Brandon Woodruff", "score2"]
BWmilARa   <- MLB2018[MLB2018$pitcher2=="Brandon Woodruff", "score1"]
BWmilRMELT <- melt(c(BWmilHRs, BWmilARs), na.rm = TRUE)
BWmilAMELT <- melt(c(BWmilHRa, BWmilARa), na.rm = TRUE)
BWmilRs    <- data.frame(BWmilRMELT$value)
BWmilRa    <- data.frame(BWmilAMELT$value)

#Jhoulys Chacin
JCmilHRs   <- MLB2018[MLB2018$pitcher1=="Jhoulys Chacin", "score1"]
JCmilHRa   <- MLB2018[MLB2018$pitcher1=="Jhoulys Chacin", "score2"]
JCmilARs   <- MLB2018[MLB2018$pitcher2=="Jhoulys Chacin", "score2"]
JCmilARa   <- MLB2018[MLB2018$pitcher2=="Jhoulys Chacin", "score1"]
JCmilRMELT <- melt(c(JCmilHRs, JCmilARs), na.rm = TRUE)
JCmilAMELT <- melt(c(JCmilHRa, JCmilARa), na.rm = TRUE)
JCmilRs    <- data.frame(JCmilRMELT$value)
JCmilRa    <- data.frame(JCmilAMELT$value)


#Rockies

COL18H <- subset(MLB2018, team1 == "COL", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

COL18A <- subset(MLB2018, team2 == "COL", select = c(date, playoff, season, team1, team2, pitcher1, pitcher2, score1, score2))

COLRHRs    <- MLB2018[MLB2018$team1=="COL", "score1"]
COLRHRa    <- MLB2018[MLB2018$team1=="COL", "score2"]
COLRARs    <- MLB2018[MLB2018$team2=="COL", "score2"]
COLRARa    <- MLB2018[MLB2018$team2=="COL", "score1"]
COLRsMELT  <- melt(c(COLRHRs, COLRARs), na.rm = TRUE)
COLRaMELT  <- melt(c(COLRHRa, COLRARa), na.rm = TRUE)
COLRs      <- data.frame(COLRsMELT$value)
COLRa      <- data.frame(COLRaMELT$value)

#Rockies PITCHERS
#Antonio Senzatela
AScolHRs   <- MLB2018[MLB2018$pitcher1=="Antonio Senzatela", "score1"]
AScolHRa   <- MLB2018[MLB2018$pitcher1=="Antonio Senzatela", "score2"]
AScolARs   <- MLB2018[MLB2018$pitcher2=="Antonio Senzatela", "score2"]
AScolARa   <- MLB2018[MLB2018$pitcher2=="Antonio Senzatela", "score1"]
AScolRMELT <- melt(c(AScolHRs, AScolARs), na.rm = TRUE)
AScolAMELT <- melt(c(AScolHRa, AScolARa), na.rm = TRUE)
AScolRs    <- data.frame(AScolRMELT$value)
AScolRa    <- data.frame(AScolAMELT$value)

```
#&nbsp;
####Sabermetric Win Percentage
```{r}
print.noquote("Brewers")
sabermtrkk.WP(MILRs, MILRa)
print.noquote("Rockies")
sabermtrkk.WP(COLRs, MILRa)
```
#&nbsp;

```{r}
boxplot(c(COLRa, MILRa, COLRs, MILRs), horizontal = TRUE, names = c("COL.RA", "MIL.RA", "COL.Rs", "MIL.Rs"), main = "Miluake and Colorado '18 Season", sub = "Runs Scored vs. Runs Allowed", col = c( "#33006F", "#0A2351", "#33006F", "#0A2351"), notch = TRUE, outline = FALSE, border = "#85714D")
```


```{r}
#Brewers Vs. Rockies 2018
MIL18COL     <- mlb_elo %>%
  select(date, season, playoff, team1, team2, pitcher1, pitcher2, score1, score2) %>%
  filter(team1 == "MIL") %>%
  filter(team2 == "COL") %>%
  filter(season == "2018") %>%
  select(date, team1, team2, pitcher1, pitcher2, score1, score2)

COL18MIL     <- mlb_elo %>%
  select(date, season, playoff, team1, team2, pitcher1, pitcher2, score1, score2) %>%
  filter(team1 == "COL") %>%
  filter(team2 == "MIL") %>%
  filter(season == "2018") %>%
  select(date, team1, team2, pitcher1, pitcher2, score1, score2)

MILvCOL      <- melt(c(MIL18COL$score1, COL18MIL$score2))

COLvMIL      <- melt(c(COL18MIL$score1, MIL18COL$score2))
```
#&nbsp;

```{r}
boxplot(c(COLvMIL, MILvCOL), horizontal = TRUE, names = c("COL", "MIL"), main = "Brewers vs Rockies '18", sub = "Runs Scored against eachother", col = c("#33006F", "#0A2351"), border = "#85714D")

```

#&nbsp;

###Thursday @Miller Park
####*Brandon Woodruff (MIL) vs. Antonio Senzatela(COL)*

```{r}
print.noquote("Brandon Woodruff")
sabermtrkk.WP(BWmilRs, BWmilRa)
print.noquote("Antonio Senzatela")
sabermtrkk.WP(AScolRs, AScolRa)
```

######***PREDICT: BREWERS WIN***

###Firday @Miller Park
####*Jhoulys Chacin (MIL) vs. Tyler Anderson (COL)*

```{r}
print.noquote("Jhoulys Chacin")
PitcherSBWsea.KBS("Jhoulys Chacin", "2018")
print.noquote("Tyler Anderson")
PitcherSBWsea.KBS("Tyler Anderson", "2018")
```

######***PREDICT: BREWERS WIN***

#&nbsp;

###Sunday @Coors Field
####*Wade Miley (MIL) vs. German Marquez (COL)*

```{r}
print.noquote("Wade Miley")
PitcherSBWsea.KBS("Wade Miley", "2018")
print.noquote("German Marquez")
PitcherSBWsea.KBS("German Marquez", "2018")
```

######***PREDICT: BREWERS WIN***

#&nbsp;

###Monday @Coors Field
####*TBD (MIL) vs. Kyle Freeland (COL)*

```{r}
print.noquote("TBD")
print.noquote("TBD")
print.noquote("Kyle Freeland")
PitcherSBWsea.KBS("Kyle Freeland", "2018")
```

######***PREDICT: ***

#&nbsp;

###Thursday @Miller Park
####*TBD (MIL) vs. TBD (COL)*

```{r}
print.noquote("TBD")
print.noquote("TBD")
print.noquote("TBD")
print.noquote("TBD")
```

######***PREDICT: ***

#&nbsp;




#&nbsp;
#&nbsp;

##***Dodgers @ Braves****

#####Series Viewer
```{r}
ATLvLAD18DS <- mlb_elo %>%
  select(date, season, playoff, team1, team2, pitcher1, pitcher2, score1, score2) %>%
  filter(playoff == "2") %>%
  filter(team1 == "ATL" | team1 == "LAD") %>%
  filter(season == "2018") %>%
  arrange(date) %>%
  select(date, team1, team2, pitcher1, pitcher2, score1, score2)

ATLvLAD18DS

```


```{r}
#Braves

ATLHRs     <- MLB2018[MLB2018$team1=="ATL", "score1"]
ATLHRa     <- MLB2018[MLB2018$team1=="ATL", "score2"]
ATLARs     <- MLB2018[MLB2018$team2=="ATL", "score2"]
ATLARa     <- MLB2018[MLB2018$team2=="ATL", "score1"]
ATLRsMELT  <- melt(c(ATLHRs, ATLARs), na.rm = TRUE)
ATLaMELT   <- melt(c(ATLHRa, ATLARa), na.rm = TRUE)
ATLRs      <- data.frame(ATLRsMELT$value)
ATLRa      <- data.frame(ATLaMELT$value)

#Braves Pitchers
#Mike Foltynewicz

MFatlHRs   <- MLB2018[MLB2018$pitcher1=="Mike Foltynewicz", "score1"]
MFatlHRa   <- MLB2018[MLB2018$pitcher1=="Mike Foltynewicz", "score2"]
MFatlARs   <- MLB2018[MLB2018$pitcher2=="Mike Foltynewicz", "score2"]
MFatlARa   <- MLB2018[MLB2018$pitcher2=="Mike Foltynewicz", "score1"]
MFatlRMELT <- melt(c(MFatlHRs, MFatlARs), na.rm = TRUE)
MFatlAMELT <- melt(c(MFatlHRa, MFatlARa), na.rm = TRUE)
MFatlRs    <- data.frame(MFatlRMELT$value)
MFatlRa    <- data.frame(MFatlAMELT$value)

#Anibal Sanchez

ASatlHRs   <- MLB2018[MLB2018$pitcher1=="Anibal Sanchez", "score1"]
ASatlHRa   <- MLB2018[MLB2018$pitcher1=="Anibal Sanchez", "score2"]
ASatlARs   <- MLB2018[MLB2018$pitcher2=="Anibal Sanchez", "score2"]
ASatlARa   <- MLB2018[MLB2018$pitcher2=="Anibal Sanchez", "score1"]
ASatlRMELT <- melt(c(ASatlHRs, ASatlARs), na.rm = TRUE)
ASatlAMELT <- melt(c(ASatlHRa, ASatlARa), na.rm = TRUE)
ASatlRs    <- data.frame(ASatlRMELT$value)
ASatlRa    <- data.frame(ASatlAMELT$value)

#Dodgers

LADHRs     <- MLB2018[MLB2018$team1=="LAD", "score1"]
LADHRa     <- MLB2018[MLB2018$team1=="LAD", "score2"]
LADARs     <- MLB2018[MLB2018$team2=="LAD", "score2"]
LADARa     <- MLB2018[MLB2018$team2=="LAD", "score1"]
LADRsMELT  <- melt(c(LADHRs, LADARs), na.rm = TRUE)
LADaMELT   <- melt(c(LADHRa, LADARa), na.rm = TRUE)
LADRs      <- data.frame(LADRsMELT$value)
LADRa      <- data.frame(LADaMELT$value)

#Dodgers Pitchers

#Hyun-Jin Ryu
HRladHRs   <- MLB2018[MLB2018$pitcher1=="Hyun-Jin Ryu", "score1"]
HRladHRa   <- MLB2018[MLB2018$pitcher1=="Hyun-Jin Ryu", "score2"]
HRladARs   <- MLB2018[MLB2018$pitcher2=="Hyun-Jin Ryu", "score2"]
HRladARa   <- MLB2018[MLB2018$pitcher2=="Hyun-Jin Ryu", "score1"]
HRladRMELT <- melt(c(HRladHRs, HRladARs), na.rm = TRUE)
HRladAMELT <- melt(c(HRladHRa, HRladARa), na.rm = TRUE)
HRladRs    <- data.frame(HRladRMELT$value)
HRladRa    <- data.frame(HRladAMELT$value)

#Hyun-Jin Ryu
CKladHRs   <- MLB2018[MLB2018$pitcher1=="Hyun-Jin Ryu", "score1"]
CKladHRa   <- MLB2018[MLB2018$pitcher1=="Hyun-Jin Ryu", "score2"]
CKladARs   <- MLB2018[MLB2018$pitcher2=="Hyun-Jin Ryu", "score2"]
CKladARa   <- MLB2018[MLB2018$pitcher2=="Hyun-Jin Ryu", "score1"]
CKladRMELT <- melt(c(CKladHRs, CKladARs), na.rm = TRUE)
CKladAMELT <- melt(c(CKladHRa, CKladARa), na.rm = TRUE)
CKladRs    <- data.frame(CKladRMELT$value)
CKladRa    <- data.frame(CKladAMELT$value)
```
#&nbsp;
###Sabermetric Win Percentage

```{r}
print.noquote("Dodgers")
sabermtrkk.WP(LADRs, LADRa)
print.noquote("Braves")
sabermtrkk.WP(ATLRs, ATLRa)
```
#&nbsp;

```{r}
boxplot(c(LADRa, ATLRa, LADRs, ATLRs), horizontal = TRUE, names = c("LAD.RA", "ATL.RA", "LAD.Rs", "ATL.Rs"), main = "Dodgers and Braves 2018", sub = "Runs Scored vs. Runs Allowed", col = c( "#005A9C", "#CE1141", "#005A9C", "#CE1141"), notch = TRUE, outline = FALSE, border = "#A5ACAF")
```

#&nbsp;

```{r}
#Brewers Vs. Rockies 2018
LAD18ATL     <- mlb_elo %>%
  select(date, season, playoff, team1, team2, pitcher1, pitcher2, score1, score2) %>%
  filter(team1 == "LAD") %>%
  filter(team2 == "ATL") %>%
  filter(season == "2018") %>%
  select(date, team1, team2, pitcher1, pitcher2, score1, score2)

ATL18LAD     <- mlb_elo %>%
  select(date, season, playoff, team1, team2, pitcher1, pitcher2, score1, score2) %>%
  filter(team1 == "ATL") %>%
  filter(team2 == "LAD") %>%
  filter(season == "2018") %>%
  select(date, team1, team2, pitcher1, pitcher2, score1, score2)

LADvATL      <- melt(c(LAD18ATL$score1, ATL18LAD$score2))

ATLvLAD      <- melt(c(ATL18LAD$score1, LAD18ATL$score2))

```


```{r}
boxplot(c(ATLvLAD, LADvATL), horizontal = TRUE, names = c("ATL", "LAD"), main = "Dodgers Vs. Braves 2018", sub = "Runs Scored against eachother", col = c("#CE1141", "#005A9C"), border = "#A5ACAF")
```
#&nbsp;

####Thursday @ Dodgers Stadium
#####*Hyun-Jin Ryu vs Hyun-Jin Ryu*

```{r}
print.noquote("Hyun-Jin Ryu")
sabermtrkk.WP(HRladRs, HRladRa)
print.noquote("Mike Foltynewicz")
sabermtrkk.WP(MFatlRs, MFatlRa)
```

######***PREDICT: 65% DODGERS WIN***

#&nbsp;

####Friday @ Dodgers Stadium
#####*Clayton Kershaw vs Anibal Sanchez*

```{r}
print.noquote("Clayton Kershaw")
PitcherSBWsea.KBS("Clayton Kershaw", "2018")
print.noquote("Anibal Sanchez")
PitcherSBWsea.KBS("Anibal Sanchez", "2018")
```

######***PREDICT: DODGERS WIN***
#&nbsp;



####Sunday @ Atlanta
#####*Walker Buehler vs Sean Newcomb*

```{r}
print.noquote("Walker Buehler (LAD)")
PitcherSBWsea.KBS("Walker Buehler", "2018")
print.noquote("Sean Newcomb (ATL")
PitcherSBWsea.KBS("Sean Newcomb", "2018")
```

######***PREDICT: 54% DODGERS WIN***
#&nbsp;

####Monday @ Atlanta
#####*Rich Hill (LAD) vs Mike Foltynewicz (ATL)*

```{r}
print.noquote("Rich Hill (LAD)")
PitcherSBWsea.KBS("Rich Hill", "2018")
print.noquote("Sean Newcomb (ATL")
PitcherSBWsea.KBS("Mike Foltynewicz", "2018")
```

######***PREDICT: 61% DODGERS WIN***

#&nbsp;
#&nbsp;


#***American League Championship Series***

###Boston Red Sox vs. Houston Astros
```{r}
PSViewrrQF.KBS("BOS", "HOU", "2018", "3")
```



#&nbsp;
#&nbsp;


#***National League Championship Series***
###Miluake Brewers vs Los Angeles Dodgers

```{r}
MILvLADnlcs <- PSViewrrQF.KBS("MIL", "LAD", "2018", "3")
MILvLADnlcs
```
#&nbsp;

```{r}
boxplot(c(LADRa, MILRa, LADRs, MILRs), horizontal = TRUE, names = c("LAD.RA", "MIL.RA", "LAD.Rs", "MIL.Rs"), main = "Dodgers and Brewers 2018", sub = "Runs Scored vs. Runs Allowed", col = c( "#005A9C", "#0A2351", "#005A9C", "#0A2351"), notch = TRUE, outline = FALSE, border = "#85714D")
```
#&nbsp;

```{r}
TVTRsRaBOXPLOT.KBS("MIL", "#0A2351", "LAD", "#005A9C","Dodgers vs Brewers 2018", "Runs Scored vs. Runs Allowed", "#85714D", "2018")

```
#&nbsp;
####Sabermetric Win Percentage
```{r}
print.noquote("Dodgers")
sabermtrkk.WP(LADRs, LADRa)
print.noquote("Brewers")
sabermtrkk.WP(MILRs, MILRa)
```


#&nbsp;

####Friday @ Miller Park
#####*Clayton Kershaw vs TBD*

```{r}
print.noquote("Clayton Kershaw (LAD)")
PitcherSBWsea.KBS("Clayton Kershaw", "2018")
PitcherSBW.all.playoffs.KBS("Clayton Kershaw")
mean(c(PitcherSBWsea.KBS("Clayton Kershaw", "2018"), PitcherSBW.all.playoffs.KBS("Clayton Kershaw")))
print.noquote("Gio Gonzalez (MIL)")
PitcherSBWsea.KBS("Gio Gonzalez", "2018")
PitcherSBW.all.playoffs.KBS("Gio Gonzalez")
mean(c(PitcherSBWsea.KBS("Gio Gonzalez", "2018"), PitcherSBW.all.playoffs.KBS("Gio Gonzalez")))
```
######*** ***
#&nbsp;

####Saturday @ Miller Park
#####*Hyun-Jin Ryu vs Wade Miley*
```{r}
print.noquote("Hyun-Jin Ryu (LAD)")
PitcherSBWsea.KBS("Hyun-Jin Ryu", "2018")
PitcherSBW.all.playoffs.KBS("Hyun-Jin Ryu")
mean(c(PitcherSBWsea.KBS("Hyun-Jin Ryu", "2018"), PitcherSBW.all.playoffs.KBS("Hyun-Jin Ryu")))
print.noquote("Wade Miley (MIL)")
PitcherSBWsea.KBS("Wade Miley", "2018")
PitcherSBW.all.playoffs.KBS("Wade Miley")
mean(c(PitcherSBWsea.KBS("Wade Miley", "2018"), PitcherSBW.all.playoffs.KBS("Wade Miley")))
```
######*** ***
#&nbsp;

####Monday @ Dodger Stadium
#####*Walker Buehler vs Jhoulys Chacin*
```{r}
print.noquote("Walker Buehler (LAD)")
PitcherSBWsea.KBS("Walker Buehler", "2018")
PitcherSBW.all.playoffs.KBS("Walker Buehler")
mean(c(PitcherSBWsea.KBS("Walker Buehler", "2018"), PitcherSBW.all.playoffs.KBS("Walker Buehler")))
print.noquote("Jhoulys Chacin (MIL)")
PitcherSBWsea.KBS("Jhoulys Chacin", "2018")
PitcherSBW.all.playoffs.KBS("Jhoulys Chacin")
mean(c(PitcherSBWsea.KBS("Jhoulys Chacin", "2018"), PitcherSBW.all.playoffs.KBS("Jhoulys Chacin")))
```
#&nbsp;

####Tuesday @ Dodger Stadium
#####*Rich Hill vs Gio Gonzalez*
```{r}
print.noquote("Rich Hill (LAD)")
PitcherSBWsea.KBS("Rich Hill", "2018")
PitcherSBW.all.playoffs.KBS("Rich Hill")
mean(c(PitcherSBWsea.KBS("Rich Hill", "2018"), PitcherSBW.all.playoffs.KBS("Rich Hill")))
print.noquote("Gio Gonzalez (MIL)")
PitcherSBWsea.KBS("Gio Gonzalez", "2018")
PitcherSBW.all.playoffs.KBS("Gio Gonzalez")
mean(c(PitcherSBWsea.KBS("Gio Gonzalez", "2018"), PitcherSBW.all.playoffs.KBS("Gio Gonzalez")))
```
######***PREDICT: 54% Dodgers win***



#&nbsp;

#&nbsp;

#&nbsp;

#&nbsp;

#&nbsp;

#&nbsp;